\documentclass[linenumbers,draft]{agujournal}
\journalname{Geophysical Research Letters}

\begin{document}

\title{Advanced prediction of climate-forced changes in oceanic dissolved oxygen}

%-------------------------------------------------------------------------------
\authors{
Matthew C. Long\affil{1},
Stephen Yeager\affil{1},
others?}

\affiliation{1}{Climate and Global Dynamics Laboratory, National Center for Atmospheric Research, Boulder, Colorado, USA.}

\correspondingauthor{M. C. Long}{mclong@ucar.edu}

%-------------------------------------------------------------------------------
\begin{keypoints}
\item
\item
\item
\end{keypoints}
%-------------------------------------------------------------------------------


%-------------------------------------------------------------------------------
\begin{abstract}
%-------------------------------------------------------------------------------

%-------------------------------------------------------------------------------
\end{abstract}
%-------------------------------------------------------------------------------


%-------------------------------------------------------------------------------
\section{Introduction}
%-------------------------------------------------------------------------------

Dissolved oxygen is a fundamental constraint on the marine habitat.
When oxygen concentrations fall below ``hypoxic'' limits, organisms reliant on aerobic metabolism cannot function.
Coastal hypoxia can have significant impacts on marine ecosystems and fisheries \citep{Rabalais-Diaz-etal-2010}.
Predictive capacity would be useful.

There are good geophysical reasons to expect high predictability of dissolved oxygen anomalies with long forecast lead, because much of the variability is on multidecadal timescales.


Prediction of biogeochemical state variables in the North Pacific with CESM \citep{Chikamoto-Timmermann-etal-2015}.




%-------------------------------------------------------------------------------
\acknowledgments
%-------------------------------------------------------------------------------

This research used computing resources provided by the NCAR Computational and Information Systems Laboratory.
NCAR is supported by the National Science Foundation.


%\listofchanges

%-------------------------------------------------------------------------------
\bibliography{o2-prediction-refs.bib}
%-------------------------------------------------------------------------------

\end{document}
